Analysis of cycling potential around key corridors in Greater Manchester

### 2020-05-19 code/mcr-safe-streets-analysis.Rmd

---
title: "Analysis of cycling potential around key corridors in Greater Manchester"
author: "Robin Lovelace"
date: "18/05/2020"
# output: bookdown::html_document2
# output: bookdown::word_document2
output: bookdown::github_document2
# output: bookdown::pdf_document2
---

@@

@@

r$pt_mode_shift = r$ebike_sip * -1
# summary(r$pt_mode_shift)
# nrow(r) # 16363
# rnet_pt = stplanr::overline(r, "pt_mode_shift")
# saveRDS(rnet_pt, "mcr-rnet_pt.Rds")
# mapview::mapview(rnet_pt)
rnet_pt = readRDS("mcr-rnet_pt.Rds")

# since 2011 there has been a doubling

@@

Cycling potential can also be estimated in terms of the number of new cycling trips that could result from a mode shift to cycling.
Results of the shift from PT under the E-bikes scenario, which were calculated at the route segment level for the first time in this study, are shown for each key corridor in Figure \@ref(fig:shift):

>>>>

---
title: "Analysis of cycling potential around key corridors in Greater Manchester"
author: "Robin Lovelace"
date: "18/05/2020"
# output: bookdown::html_document2
output: bookdown::word_document2
# output: bookdown::github_document2
# output: bookdown::pdf_document2
---

@@

<!-- Summary route network results from Ebikes scenario, aggregated to the route network level, are shown for Greater Manchester below -->

@@

r$pt_mode_shift = r$ebike_sip * -1
# summary(r$pt_mode_shift)
# nrow(r) # 16363
# rnet_pt = stplanr::overline(r, "pt_mode_shift")
# saveRDS(rnet_pt, "mcr-rnet_pt.Rds")
# mapview::mapview(rnet_pt)
rnet_pt = readRDS("mcr-rnet_pt.Rds")
# summary(rnet_pt$pt_mode_shift)
rnet_pt_high = rnet_pt %>% filter(pt_mode_shift > 20)
# mapview::mapview(rnet_pt_high)
# since 2011 there has been a doubling

@@

Results of the shift from PT under the E-bikes scenario, which were calculated at the route segment level for the first time in this study, are shown for each key corridor in Figure \@ref(fig:shift):
